---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Lab report #1

Follow the instructions posted at https://ds202-at-isu.github.io/labs.html for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.  

All submissions to the github repo will be automatically uploaded for grading once the due date is passed.
Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.

```{r}
# Croix:
library(classdata)
library(tidyverse)
```

1. Inspect the first few lines of the data set
```{r}
# Croix:
head(ames)
```

2. Is there a variable of special interest?
The variable of special interest is `Sale Price`.

3. Start the exploration with the main variable:

What is the range of the variable? Draw a histogram for a numeric variable or a bar chart, if the variable is categorical. What is the general pattern? Is there anything odd? 
-Keegan: There is a skew right and there are a couple outliers that cost way more than the rest of the prices.
```{r}
library(ggplot2)
library(classdata)

ggplot(data=ames, aes(x=`Sale Price`)) + geom_histogram(binwidth=100000) +
  labs(title="histogram", x = "sale price", y="count")
```


4. Pick a variable that might be related to the main variable.
what is the range of that variable? plot. describe the pattern.

Variable related: TotalLivingArea (sf)
```{r}
# Croix: 
ggplot(data = ames, aes(x = `TotalLivingArea (sf)`)) + geom_histogram(binwidth = 500)
```
```{r}
# Croix:
which.min(ames$`TotalLivingArea (sf)`)
which.max(ames$`TotalLivingArea (sf)`)
```
Croix: 
The pattern of this histogram is unimodal and slightly skewed right. Values to the far right may be potential outliers. The range of this variable is from 35 square feet and 6482 square feet.


what is the relationship to the main variable? plot a scatterplot, boxplot or facetted barcharts (dependening on the types of variables involved). Describe overall pattern, does this variable describe any oddities discovered in 3? Identify/follow-up on any oddities.
```{r}

```


Ji Xian Fu - Procedure:
The main variable for this exploration is Sale Price. As a team, do steps 1 through 3. Document your findings in the README.Rmd of the lab's repo.

As a team, discuss different lines of investigation (step 4) and agree on who is doing which investigation. Make a note of who is doing what in the README.Rmd

Individually: follow through with your line of investigation. Include at least one plot that describes the relationship between sales prices and your variable. Include one paragraph describing the pattern you see. Are there oddities? Follow-up on (some of) them.
